You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-25 paper/paper_wei.tex
add a bit into paper about dict-base baseline

Identical meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.  
Although two utternaces may be semantically equivelant, they can still be stylistically quite different.  For example, the same information
is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.

In this paper, we investigate the task of automatic paraphrasing when targeting a writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
We exploit modern translations of 17 plays written to help students better understand Shakespeare's work.  A parallel corpus is extracted from these modern translations,
which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakesperean English.  In addition we develop several
baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in Shakesperean english, or parallel monolingual text
gathered through Amazon's Mechanical Turk \cite{chen11}.

@@

Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications, for example helping students to experiment with writing literature in the
style of authors they are studying.  Additionally note that out of the 37 surviving plays written by William Shakespeare, only 17 currently have modern translations available; although we have not yet formally evaluated
paraphrasing in the other direction, we believe this work also has the potential to make the other 20 plays more accessable to students of Shakespeare by automatically generating relatively high-quality modern translations.

@@

\section{Data}
We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
of modern translations and dictionaries of stylistically representative words and their modern equivelants.

We compare 3 different stylisitic paraphrase systems targeting Shakesperean English.  One which leverages parallel corpora of modern translations, another which makes use
of dictionaries of styalistically representative expressions, and another which leverages out-of-domain monolingual parallel data.

@@

After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.  The modern translations from each source are qualitatively quite
different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the enotes translations are much more conservative, making fewer changes.
To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
original text; the Sparknotes paraphrases result in a BLEU score of 24.67, whereas the Enotes paraphrases prouce a much higher BLEU of 52.30 indicating their similarity to the original text.
These corpus statistics are summarized in table \ref{corpus_stats}.

@@

\subsection{Baselines}
Phrase-based translation has been demonstrated to be an effective approach to generating paraphrses \cite{chen11,quirk04}, however this approach does require the existence of
parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches.

\subsubsection{Dictionary Based Paraphrase}
\label{dictionary_baseline}
Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{Koehn00}.

We gathered a set of 2,386  dictionary entries which were scraped from \url{http:/www.william-shakespeare.info} and semi-automaticaly cleaned.  Example
dictionary entries are presented in table \ref{dictionary_example}.

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l||l|l|}
    \hline
    target & source & target & source \\
    \hline
    \hline
    ABATE & shorten & ANIGHT & by night \\
    \hline
    CAUTEL & deceit & CHILDING & pregnant \\
    \hline
    FOIL & defeat & MORTAL & deadly \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Exaple dictionary entries}
  \label{dictionary_example}
\end{table}

\subsubsection{Out of Domain Monolingual Parallel Data}
As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
language model consisting of Shakespeare's 37 plays.  Although this monolingual parallel data does not include text in the target writing style,
the in-domain language model does bias the generated sentences towards Shakespeare's writing style.

@@

\section{Human Evaluation}
Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is innitially unclear how well the BLEU and PINC
automatic evaluation metrics perform when applied to evaluating paraphrases targeting a specific style of writing.  BLEU and PINC have previously
been shown to have high correlation with human judgements of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
previous work has evaluated automatically generated paraphrases which target a specific style of writing \cite{chen11}.

While BLEU is typically used to measure semantic adequacy, it seems reasonable to assume that it may also depend on style, since utterances
are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU doesn't tell us, however
is what portion of it's improvements are due to stylistic similarity or semantic equivelance.  For this reason, we were motivated perform
an evaluation based on human judgements of semantic adequacy, lexical dissimilarity and stylistic similarity.

For this purpose, we randomly sampled 100 lines from Romeo and Juliet, then two of the authors annotated each sentence and it's Shakesperean
translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overal quality.
The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.

\begin{figure}
  \begin{center}
    \includegraphics[width=4in]{figures/human_judgements.pdf}
  \end{center}
  \caption{Average human judgements evaluating semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality
    of Shakesperean paraphrase systems} 
  \label{human_judgements}
\end{figure}

%Argue why BLEU might capture writing style in addition to semantic adequacy
%Argue that we really want to seperate these two measures
%Present initial results from human evaluation (plot? - table?)
%Plot style vs. equivelance...?

\section{New Metrics Evaluating Writing Style}

>>>>

Identical meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
fundamental to many natural language understanding tasks \cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.  
Although two utterances may be semantically equivalent, they can still be stylistically quite different.  For example, the same information
is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.

In this paper, we investigate the task of automatic paraphrasing when targeting a writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
We exploit modern translations of 17 plays written to help students better understand Shakespeare's work.  A parallel corpus is extracted from these modern translations,
which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakesperean English.  In addition we develop several
baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in Shakesperean english, or parallel monolingual text
gathered through crowd sourcing platforms such as Amazon's Mechanical Turk \cite{chen11}.

@@

Systems which are capable of automatically paraphrasing literary writing styles could be directly beneficial for educational applications, for example helping students to experiment with writing literature in the
style of authors they are studying.  Additionally note that out of the 37 surviving plays written by William Shakespeare, only 17 currently have modern translations available; although we have not yet formally evaluated
paraphrasing in the other direction, we believe this work also has the potential to make the other 20 plays more accessible to students of Shakespeare by automatically generating relatively high-quality modern translations.

@@

\section{Data}
We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
of modern translations and dictionaries of stylistically representative words and their modern equivalents.

We compare 3 different stylistic paraphrase systems targeting Shakesperean English.  One which leverages parallel corpora of modern translations, another which makes use
of dictionaries of stylistically representative expressions, and another which leverages out-of-domain monolingual parallel data.

@@

After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the Enotes data.  The modern translations from each source are qualitatively quite
different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the Enotes translations are much more conservative, making fewer changes.
To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
original text; the Sparknotes paraphrases result in a BLEU score of 24.67, whereas the Enotes paraphrases prouce a much higher BLEU of 52.30 indicating their similarity to the original text.
These corpus statistics are summarized in table \ref{corpus_stats}.

@@

\subsection{Baselines} po
Phrase-based translation has been demonstrated to be an effective approach to generating paraphrases \cite{chen11,quirk04}, however this approach does require the existence of
parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches.

\subsubsection{Dictionary Based Paraphrase}
\label{dictionary_baseline}
Several dictionaries of stylistically representative words of Shakesperean English and their modern equivalents are available on the web.  These dictionaries can be used 
to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{Koehn00}.

We gathered a set of 20,138 dictionary entries which were scraped from \url{http://www.shakespeareswords.com/}, then used heuristic rules to extract 68,709 phrase/word pairs.  Example
dictionary entries are presented in table \ref{dictionary_example}. As described in \cite{Koehn00}, we estimate phrase translation probabilities based on the frequencies of the translation words/phrases in the target language - the Shakespearean English.

For instance, if we look at the modern English (*probably define EME, Shakespearean, modern/ordinary etc ... I don't know what words to use) word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. We can obtain the following conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 36 plays by SRILM toolkit (*ref "SRILM an Extensible Language Modeling Toolkit":

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|}
    \hline
    target & source \\
    \hline
    \hline
    CRAVE & beg, entreat, request \\
    \hline
    GAGE & pledge, challenge \\
    \hline
    HAPLY & perhaps, maybe, by chance, with luck \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Example dictionary entries}
  \label{dictionary_example}
\end{table}

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|||}
    \hline
    conditional probability & target & source \\
    \hline
    \hline
    0.0000790755 & PERCHANCE & maybe \\
    \hline
    0.00003691883 & PERADVENTURE & maybe \\
    \hline
    0.00007524298 & HAPLY & maybe \\
    \hline
    0.00007141065 & HAPPILY & maybe \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Word frequency in target language}
  \label{word_frequency}
\end{table}

\subsubsection{Out of Domain Monolingual Parallel Data}
As a final baseline we consider a paraphrase system which is trained on out-of-domain parallel data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  (*Maybe describe a bit more of the strength of Chen et al.'s data?) We combine a phrase table extracted from this out-of-domain parallel text, with an in-domain
language model consisting of Shakespeare's 37 (*should be 36? hold out) plays.  Although this monolingual parallel data does not include text in the target writing style,
the in-domain language model does bias the generated sentences towards Shakespeare's writing style.

@@

\section{Evaluation Metrics}
\begin{itemize}
  \item Describe the need for automatic evaluation metrics.
  \item Describe previously used evaluation metrics for paraphrase.
  \item Highlight problems with previous metrics when targeting a specific writing style.
  \item Propose new metrics.
\end{itemize}
